Results

### 2019-05-02 analysis/survey/preregistration.Rmd
Fix list indentation
Fix incorrect TeX

where $y$ = choice to donate, $X$ = design matrix of attribute levels, $\beta$ = latent individual preferences, $\Z$ = SOMETHING, $\Gamma$ = individual covariates, and $\varepsilon$ and $\xi$ = errors.

>>>>

where $y$ = choice to donate, $X$ = design matrix of attribute levels, $\beta$ = latent individual preferences, $Z$ = SOMETHING, $\Gamma$ = individual covariates, and $\varepsilon$ and $\xi$ = errors.
